Supplementary Material

### 2021-01-25 paper/ifo-complexAudio.tex
starting to move material around for referee response

In this section, we explore how this demonstration can be used to teach a selection of signal processing techniques.
The apparatus used in Sections~\ref{sec:ifo} to~\ref{sec:viterbi_wandering} allows undergraduate students to explore a range of signal processing techniques and filters of interest and provides a foundation for many technical applications~\cite{DigitalProcingOfSpeechSignals:1978}. 
We provide a series of example activities using complex audio (such as music and speech) as a natural successor to constant and wandering tones. 
As complex audio signals are not quasi-monochromatic, unlike continuous gravitational-wave signals, the Viterbi algorithm as implemented in Section~\ref{sec:viterbi_wandering} is not directly applicable here. 
Instead, in this section, we use the interferometer as an optical microphone to detect and playback complex audio signals (i.e.\ using light to capture sound).
In doing so, we experiment with a hierarchy of passive filters which suppress noise, yet make no assumption about the specific form of the signal, unlike the Fourier-based maximum likelihood matched filter which is tuned to the sinusoidal signals in Section~\ref{sec:single_tone} and Appendix~\ref{app:sinusoid_likelihood}.
A vast literature exists on signal processing with speech, see Ref.~\cite{DigitalProcingOfSpeechSignals:1978} for introductory material including Fourier analysis and digital representations.
Optical microphone devices have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defence industry and operate on a variety of related principles.

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_spectrum_melatos.pdf}
	\caption{Spectrum of optical microphone recording of the same adult male voice in Fig.~\ref{fig:logMMSE_timeseries} showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude 2 which otherwise dominate the plot. The change in scale from the top panel is not of concern as the ear hears the relative frequency content and normalisation of the time series fixes any scaling. The bottom two panels also show a broad feature from around $750\,{\rm Hz}$ to $1200\,{\rm Hz}$, the origin of which is yet to be determined.}
	\label{fig:logMMSE_spectrum}
\end{figure*}
\end{comment}

>>>>

In this section, we explore how this demonstration can be used to teach a selection of signal processing techniques. 
We use complex audio signals (such as music and speech) as a natural successor to the constant and wandering tones used in Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering} respectively.
As complex audio signals are not quasi-monochromatic, the Viterbi algorithm as applied in Section~\ref{sec:viterbi_wandering} is not directly applicable here. 
Instead we use a hierarchy of passive filters which suppress noise, yet make no assumption about the specific form of the signal, unlike the Fourier-based maximum likelihood filter which is tuned to the sinusoidal signals in Section~\ref{sec:single_tone} and Appendix~\ref{app:sinusoid_likelihood}.

Here we treat the Michelson interferometer as an optical microphone, where a laser beam is used to detect sound vibrations. 
Optical microphone devices have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defence industry and operate on a variety of related principles.
Our objective is to play a recording of speech or music through the speaker attached to mirror M1 (see Fig.XXXX), record the interference pattern, and then recover the original signal via a selection of signal processing techniques.

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
Instead, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
A selection of filters are applied to the data, details of which are presented in Supplementary Material and we present the results of the best performing filters in Section~\ref{sec:opticalMicResults}. \han{rephrase depending on what we show.}

\subsection{Hardware modifications for the optical microphone}
\label{sec:initialResultsOpMic}
The human ear can hear frequencies in the range of $\sim 20\,{\rm Hz}$--$20\,{\rm kHz}$. 
Speech intelligibility (being able to understand speech) requires frequencies up to $3\,{\rm kHz}$ and music requires up to and beyond $8\,{\rm kHz}$~\cite{speech_intelligibility}. Therefore, the optical microphone requires a sample rate of at least $16\,{\rm kHz}$ to capture both speech and music (adjusting for the Nyquist frequency). 
This cannot be achieved with the webcam used in Sections~\ref{sec:single_tone} and ~\ref{sec:viterbi_wandering} as it has a sampling rate of $30\,{\rm Hz}$ and thus can only ``hear'' frequencies below $15\,{\rm Hz}$.
To overcome this issue, we use a photodiode\footnote{A photodiode is an electrical component that acts as a regular diode when no light is incident on it, blocking any current flow in the reverse direction. As the intensity of incident light rises, it becomes increasingly conductive in the reverse direction.} at the output of the interferometer to achieve a sampling rate of $16\,{\rm kHz}$.

%An updated schematic and a photograph of the entire optical microphone are shown in the left and right panels of Fig.~\ref{fig:ifo_schematic_podo}, respectively.
See Appendix~\ref{app:circuit_diagram} for a diagram and photograph of the circuit. 
\han{[Hannah] I've removed the second schematic and photo for now - could be an option for the photo to go in the appendix / supplement if we want to show the physical set up?}

%The source audio was played through the speaker with the optical microphone recording for the full duration of the audio (around a minute long for most sources). 
We test the optical microphone with a variety of recordings, including speech from different people and music ranging from simple melodies and rhythms to songs. During recordings, care is taken to minimise activity around the demonstration to reduce environmental noise coupling into the interferometer. 
The timeseries data is then directly converted to a .wav file and played as an audio recording using the \texttt{scipy.io.wavfile.write} function in Python~\cite{scipy,python}. 
When processing the results, we restrict our analysis to only the first $10\,{\rm s}$ of each observation (for efficiency), and only plot the first second here.

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/psd_butterworth_14_6.pdf}
	\caption{\label{fig:psd_noise}
\han{If we do not cover the butterworth filter in the main text, I'd suggest only showing the top panel of this figure in the main text. We can include the twp panel version in the butterworth section of the supplementary material}
Top: power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white. 
After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

\subsection{Optical microphone results}
\label{sec:opticalMicResults}
\han{[Hannah] keen to hear other's thoughts, but I think it would be cool to show the notch+wiener combined and the logmmse as the results? They could be placed in a single figure for ease of comparison with time \& spectrum columns and rows: 1. original signal, 2. raw output, 3. combined cascaded notch and Wiener, 4. logMMSE}

We explore several filters to remove the $50\,{\rm Hz}$ mains hum and harmonics, and also to improve speech intelligibility of the recording. 
The accompanying supplementary material describes a range of analysis techniques which can be used as examples for the undergraduate laboratory. 
All filters are tested on the same $1\,{\rm s}$ long speech recording.

In signal processing, the ideal filter would be one that:
i) completely attenuates the undesired parts of the spectrum, 
ii) does not change the rest of the spectrum, and 
iii) smoothly transitions between these regions, as to not damage the time domain signal when seen under convolution. 
However, these three conditions cannot all hold at once and any filter must compromise between them. \han{[Notes] editor's comments suggest expanding on this?}
Here we present results of two analysis.
They are briefly described and the results shown (see Supplementary Material for details).

Firstly, we consider two signal processing techniques used in combination: the cascaded notch and Wiener filter. 
A notch filter remove signals within a specific frequency range \han{ref}. 
In our case, we would like to remove the $50\,{\rm Hz}$ mains noise and harmonics. 
Therefore, we use a cascaded notch filter where each notch is centred at each of the harmonics. 
The Wiener filter is an advanced statistical technique which makes used of statistical information from the speech data and noise. 
It amplifies parts of the signal with high SNR while suppressing pares with low SNR.

\han{refer to figure.. } shows our results.
We find that the combined cascaded notch and Wiener filter produces a better result than either alone. 
Most of the mains noise is removed, however the recovered voice sounds muffled and is not understandable.

Secondly, we apply a speech enhancement technique. 
Ref.~\cite{SubjectiveComparison} compares $13$ speech enhancement methods, finding the log minimum mean-square-error (logMMSE) estimator to be the best, qualitatively, at recovering speech (see also Ref.~\cite{Ephraim1984SpeechEU_logMMSE} for details on the logMMSE estimator). 
We use an existing implementation of the logMMSE~\cite{logmmse}.

\han{refer to figure} 
After applying the logMMSE estimator we see significant attenuation of the mains harmonics and a general smoothing of the spectrum. 
Most of the background noise is removed, however the logMMSE does not significantly enhance the speech as the voice sounds muffled and indistinct.
We find some improvement with music over speech. 
Simple chords and drums can be heard, however more composite sounds and complex melodies cannot be heard clearly. 
Our observations suggest that this is especially true for certain instruments, in particular flutes and violins sometimes can’t be heard at all. 
This could be a perceptual effect or a frequency dependence somewhere in the optical microphone.
Speculating, perhaps the speaker-mirror coupling is stronger at low frequencies and thus instruments like electric bass and drums are louder in the results.
To address these problems, we need to determine whether the signals that are audibly missing (the diction in the speech and complex melodies in music) are indeed being transmitted through the optical microphone at all. 
To determine this requires a better understanding of the system, as discussed in Section~\ref{sec:future_work}.

\begin{comment} 
In this section, we explore how this demonstration can be used to teach a selection of signal processing techniques.
The apparatus used in Sections~\ref{sec:ifo} to~\ref{sec:viterbi_wandering} allows undergraduate students to explore a range of signal processing techniques and filters of interest and provides a foundation for many technical applications~\cite{DigitalProcingOfSpeechSignals:1978}. 
We provide a series of example activities using complex audio (such as music and speech) as a natural successor to constant and wandering tones. 
As complex audio signals are not quasi-monochromatic, unlike continuous gravitational-wave signals, the Viterbi algorithm as implemented in Section~\ref{sec:viterbi_wandering} is not directly applicable here. 
Instead, in this section, we use the interferometer as an optical microphone to detect and playback complex audio signals (i.e.\ using light to capture sound).
In doing so, we experiment with a hierarchy of passive filters which suppress noise, yet make no assumption about the specific form of the signal, unlike the Fourier-based maximum likelihood matched filter which is tuned to the sinusoidal signals in Section~\ref{sec:single_tone} and Appendix~\ref{app:sinusoid_likelihood}.
A vast literature exists on signal processing with speech, see Ref.~\cite{DigitalProcingOfSpeechSignals:1978} for introductory material including Fourier analysis and digital representations.
Optical microphone devices have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defence industry and operate on a variety of related principles.

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_spectrum_melatos.pdf}
	\caption{Spectrum of optical microphone recording of the same adult male voice in Fig.~\ref{fig:logMMSE_timeseries} showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The spectrum shows only a detail of the total frequency domain (there is little activity at higher frequencies) and has truncated peaks at amplitude 2 which otherwise dominate the plot. The change in scale from the top panel is not of concern as the ear hears the relative frequency content and normalisation of the time series fixes any scaling. The bottom two panels also show a broad feature from around $750\,{\rm Hz}$ to $1200\,{\rm Hz}$, the origin of which is yet to be determined.}
	\label{fig:logMMSE_spectrum}
\end{figure*}
